Can Auxiliary Indicators Improve COVID-19 Forecasts and Hotspot Prediction?

### 2021-06-13 forecast/paper/paper.tex
FINISH edits thru methods

\begin{figure}[tb!]
\centering
\includegraphics[width=\columnwidth]{fig/trajectory.pdf}
\caption{Forecasts and observed cases for HRR x. TODO 
  \attn{Create a figure here for 1 HRR. Show the fan for the quantiles.}}  
\label{fig:trajectory}
\end{figure}

@@

For forecasting, we evaluate the probabilistic forecasts produced by the
quantile models \eqref{eq:forecast_ar}, \eqref{eq:forecast_ar_x} using
\textit{weighted interval score} (WIS), which is a well-known quantile-based
scoring rule; see, e.g., \cite{Gneiting:2007}.  WIS is a proper score, which
means that its expectation is minimized by the true quantiles of the target
variable.  The use of WIS in scoring COVID-19 forecasts is discussed by
\cite{Bracher:2021}; and WIS serves as the primary metric for forecast
evaluation in the COVID-19 Forecast Hub.

WIS is typically defined for quantile-based forecasts where the quantile levels
are symmetric around 0.5.  This is the case for our choice in
\eqref{eq:quantile_levels}.  Let $F$ be a forecaster comprised of predicted
quantiles $q_\tau$ parametrized by a quantile level $\tau$.  In the symmetric
case, this is equivalent to a collection of central prediction intervals
$(\ell_\alpha, u_\alpha)$, parametrized by an exclusion probability $\alpha$. 
The WIS of the forecaster $F$, evaluated at the target variable $Y$, is defined
by  
\begin{equation}
\label{eq:wis_intervals}
\WIS(F,Y) = \sum_\alpha \Big\{\alpha(u_\alpha - \ell_\alpha) + 2 \cdot
\dist(Y, [\ell_\alpha, u_\alpha])\Big\},  
\end{equation}
where $\dist(a, S)$ is the distance between a point $a$ and set $S$ (the
smallest distance between $a$ and an element of $S$).  Note that, corresponding 
to \eqref{eq:quantile_levels}, the exclusion probabilities are $\alpha \in
\{0.05, 0.2, 0.5, 1\}$, resulting in 4 terms in the above sum.  By 
straightforward algebra, it is not hard to see WIS has an alternative 
representation in terms of the predicted quantiles themselves,
\begin{equation}
\label{eq:wis_quantiles}
\WIS(F,Y) = 2 \sum_\tau \phi_\tau(Y - q_\tau), 
\end{equation}
where $\phi_\tau(x) = \tau |x|$ for $x \geq 0$ and $\phi_\tau(x) = (1-\tau)
|x|$ for $x<0$, which is often called the ``tilted absolute'' loss.  While
\eqref{eq:wis_quantiles} is more general (it can accomodate asymmetric quantile
levels), the first definition \eqref{eq:wis_intervals} is usually preferred in
presentation, because the score nicely decouples into a ``sharpness'' component
(first term in each summand) and ``under/overprediction'' component (second term
in each summand).  The second form given in \eqref{eq:wis_quantiles} is
especially noteworthy in our current study as it reveals WIS is the same as the
quantile regression loss that we use to train our forecast models (in other
words, our models are fit to optimize WIS average over the training set).

For hotspot prediction, we evaluate the probabilistic classifiers produced by
the logistic models \eqref{eq:hotspot_ar}, \eqref{eq:hotspot_ar_x} using the
area under the curve (AUC) of their true positive versus false positive rate
curve (which is traced out by varying the discrimination threshold).

@@

TODO Briefly describe that we zero-fill Google-AA.

@@

\paragraph{Backfill, Nowcasting}

TODO Should we discuss the use of ``bad'' case rates as ground truth??

\paragraph{\attn{Methods section graveyard, most for Appendix}}

\begin{itemize}
\item Discuss the "how many days does the indicator buy" interpretation here or below?

\item Do we explain why regularization/CV not really helpful for both
forecasting and hotspots

\item Implementation was via quantgen, cite here?

\item some people don't like relative WIS beacuse it's no longer a
``proper score''.  directly address that here?

\item Do we talk about log loss?

\item Do we explain that we are using infinite-backfilled data?

>>>>

\begin{figure}[tb!]
\centering
\includegraphics[width=\columnwidth]{fig/trajectory.pdf}
\caption{TODO}
\label{fig:trajectory}
\end{figure}

@@

For forecasting, we evaluate the probabilistic forecasts produced by the
quantile models in \eqref{eq:forecast_ar}, \eqref{eq:forecast_ar_x} using 
\textit{weighted interval score} (WIS), a quantile-based scoring rule; see e.g.,
\cite{Gneiting:2007}.  WIS is a proper score, meaning that its expectation
is minimized by the population quantiles of the target variable.  The use of WIS
in COVID-19 forecast scoring is discussed in \cite{Bracher:2021}; WIS is also
the main evaluation metric used in the COVID-19 Forecast Hub.

WIS is typically defined for quantile-based forecasts where the quantile levels
are symmetric around 0.5.  This is the case for our choice in
\eqref{eq:quantile_levels}.  Let $F$ be a forecaster comprised of predicted
quantiles $q_\tau$ parametrized by a quantile level $\tau$.  In the case of
symmetric quantile levels, this is equivalent to a collection of central
prediction intervals $(\ell_\alpha, u_\alpha)$, parametrized by an exclusion
probability $\alpha$. The WIS of the forecaster $F$, evaluated at the target
variable $Y$, is defined by:
\begin{equation}
\label{eq:wis_intervals}
\WIS(F,Y) = \sum_\alpha \Big\{\alpha(u_\alpha - \ell_\alpha) + 2 \cdot
\dist(Y, [\ell_\alpha, u_\alpha])\Big\},  
\end{equation}
where $\dist(a, S)$ is the distance between a point $a$ and set $S$ (the
smallest distance between $a$ and an element of $S$).  Note that, corresponding 
to \eqref{eq:quantile_levels}, the exclusion probabilities are $\alpha \in
\{0.05, 0.2, 0.5, 1\}$, resulting in 4 terms in the above sum.  By 
straightforward algebra, it is not hard to see WIS has an alternative 
representation in terms of the predicted quantiles themselves:
\begin{equation}
\label{eq:wis_quantiles}
\WIS(F,Y) = 2 \sum_\tau \phi_\tau(Y - q_\tau), 
\end{equation}
where $\phi_\tau(x) = \tau |x|$ for $x \geq 0$ and $\phi_\tau(x) = (1-\tau)
|x|$ for $x<0$, which is often called the ``tilted absolute'' loss.  While
\eqref{eq:wis_quantiles} is more general (it can accomodate asymmetric quantile
levels), the first definition \eqref{eq:wis_intervals} is usually preferred in
presentation, because the score nicely decouples into a ``sharpness'' component
(first term in each summand) and ``under/overprediction'' component (second term
in each summand).  The second form given in \eqref{eq:wis_quantiles} is
especially noteworthy in our current study as it reveals WIS is the same as the
quantile regression loss that we use to train our forecasting models (i.e., our
models are fit to optimize WIS averaged over the training set).

For hotspot prediction, we evaluate the probabilistic classifiers produced by
the logistic models in \eqref{eq:hotspot_ar}, \eqref{eq:hotspot_ar_x} using the 
area under the curve (AUC) of their true positive versus false positive rate
curve (which is traced out by varying the discrimination threshold).

The primary aggregation scheme that we will use in model evaluation and
comparisons will be to average WIS per forecaster per ahead value $a$, over all
forecast dates $t$ and locations $\ell$; and similarly, to compute AUC per
classifier and per ahead value $a$, over all forecast dates $t$ and locations
$\ell$.

@@

Over the prediction period, all auxiliary indicators are available (in the
proper vintage sense) for all locations and prediction times, except for the
Google-AA signal, which is only observed for an average of 105 (of 306) HRRs.
This is due to the fact that that the COVID-19 search trends data is released
after applying differential privacy techniques \cite{Bavadekar:2020}, and a
missing signal value means that the level of noise added in the differential
privacy mechanism is high compared to the underyling search count.  In other
words, values of the Google-AA signal are clearly \textit{not} missing at
random.  It seems most appropriate to impute missing values by zero, and this 
is what we do in our analysis.

\paragraph{Backfill and Nowcasting}

As described previously, the auxiliary indicators defined in terms of medical
claims, CHNG-CLI, CHNG-COVID, and DV-CLI, undergo a significant and systematic
pattern of revision, or ``backfill'', after their initial publication.  Given
their somewhat statistically-regular backfill profiles, it would be reasonable
to attempt to estimate their finalized values based on vintage data---a problem
we refer to as \textit{nowcasting}---as a pre-processing step before using them
as features in the models in \eqref{eq:forecast_ar_x}, \eqref{eq:hotspot_ar_x}. 
Nowcasting is itself a highly nontrivial modeling problem, and we do not attempt
it in this paper (though it is a topic of ongoing work in our research group).
We do note, however, that this would likely improve the performance of the
models involving claims-based indicators in particular.

@@

Some signals display a significant degree of spatial heterogeneity, by which we
mean the values that they take at different geographic locations are not 
comparable.  This is true of the Google-AA signal (due to the way in which the 
underlying search trends time series is self-normalized, see
\cite{GoogleSymptoms}) and of the claims-based signals (see the discussion in
our companion paper on the API and database).  Such spatial heterogeneity likely
hurts the performance of the predictive models that rely on these signals,
since the models are trained by pooling data from all locations.  In this paper,
we do not attempt to address this issue (it is again a topic of ongoing work in
our research group), and we simply note that location-specific effects (or 
pre-processing to remove spatial bias) would likely improve the performance of
the models involving Google-AA and the claims-based indicators.
